Examining background gene lists in clusterProfiler - RNA-seq example

### 2024-05-31 analysis/analyse_rnaseq.Rmd
show enrichment and logpval discrepancy

@@

>>>>

res1 %>%
  kbl(row.names = TRUE, caption="all results") %>%
  kable_paper("hover", full_width = F)

@@

## Make charts showing changes in pvalues

For bulk RNA-seq data set #1, run enrichment with all the gene set libraries.

```{r,charts1}

names(gs)

lapply(1:length(gs), function(i) {
  bad <- orabad(d[[1]],gs[[i]])
  good <- oragood(d[[1]],gs[[i]])
  compare_ora_plots(bad,good)
} )
